The 4th Workshop on Sustainable Software: Best Practices and Experiences (WSSSPE4)

### 2016-06-10 WSSSPE4_proposal/WSSSPE4_proposal.tex
finished out Kyle's prior NSF support; possibly too long

{\bf Kyle E. Niemeyer}
is currently supported by the NSF under NSF ACI-1535065, ``SI2-SSE: Collaborative Research: An Intelligent and Adaptive Parallel CPU\slash GPU Co-Processing Software Library for Accelerating Reactive-Flow Simulations,'' made to Oregon State University for \$285,487 for the period of 1 Sept.~2015 to 31 Aug.~2018 (estimated).

This award has thus far resulted in one journal article under review~\cite{Niemeyer:2016}, one conference paper~\cite{Niemeyer:2015}, one meeting poster~\cite{SI2-poster:2016}, one software package~\cite{pyJac-v1.01}, and one manuscript in preparation~\cite{Curtis:2016}.

\textbf{Intellectual Merit:} 
\textbf{Broader Impacts:} 
\textcolor{red}{todo...}

>>>>

{\bf Kyle E. Niemeyer}
is currently supported by the NSF under NSF ACI-1535065, ``SI2-SSE: Collaborative Research: An Intelligent and Adaptive Parallel CPU\slash GPU Co-Processing Software Library for Accelerating Reactive-Flow Simulations,'' made to Oregon State University for \$285,487 for the period of 1 Sept.~2015 to 31 Aug.~2018 (estimated).
The overall goal of this project is creating a software library to accelerate the solution of chemical kinetics equations in reactive-flow simulations on hybrid computing hardware.
This will be achieved through the development of software components that include (1) integration algorithms for operation on parallel processors (e.g., vectorized CPUs, GPUs), (2) a stiffness detection metric used to adaptively select the most efficient solver based on local conditions, and (3) a computational cell clustering strategy to group similar spatial locations.
These will be incorporated into a usable, sustainable software library: SLACKHA (Software Library for Accelerating Chemical Kinetics on Hybrid Architectures).
This award has thus far resulted in one journal article under review~\cite{Niemeyer:2016}, one conference paper~\cite{Niemeyer:2015}, one meeting poster~\cite{SI2-poster:2016}, one software package~\cite{pyJac-v1.01}, and one manuscript in preparation~\cite{Curtis:2016}.
\textbf{Intellectual Merit:} The complexity of detailed chemical models prevents their use in high-fidelity computational fluid dynamics. The software library developed through this project will allow studies that are currently impractical due to computational demands; it will also shorten the design cycle of engines and combustors by reducing the time needed for design simulations.
\textbf{Broader Impacts:} This work will provide important software tools for designers to help create next-generation clean and efficient engine technology, and for researchers to study difficult problems in combustion.
In addition, the software elements developed in this program are widely applicable to computational modeling problems outside of combustion, including astrophysics, atmospheric chemistry, biochemical networks, and even cardiac electrophysiology.
%By enabling the implementation of accurate and realistic chemical models into simulations, new concepts and solutions to existing problems may be explored rapidly and at lower cost.
